% arara: lualatex
% arara: bib2gls
% arara: lualatex
% arara: lualatex
\documentclass[toc=listof]{scrreport}

\usepackage{fontspec}
\setmainfont{Linux Libertine O}
\usepackage
 [
%   debug=showwrgloss
 ]{texjavahelp}

\hypersetup{colorlinks,linkcolor=blue}
\graphicspath{{images/}}

\TJHRequireIcons{texjavahelplibicons}{16}{24}

\newcommand{\Jmakepdfx}{Jmakepdfx}

\title{\Jmakepdfx}
\author[Nicola L.C. Talbot]{Nicola L.C. Talbot\\\href{https://www.dickimaw-books.com/}{\nolinkurl{dickimaw-books.com}}}

\TeXJavaHelpLoadResources{jmakepdfx,jmakepdfx-dict}

\begin{document}
\maketitle

\frontmatter
\tableofcontents

\mainmatter
\chapter{Introduction}
\label{sec:intro}

\Jmakepdfx\ is a Java \gls{GUI} front-end application that uses GhostScript to convert
PDF files to PDF/X compliant. This application comes with NO
WARRANTY. In order to use this application you need to have both
Java (at least JRE~8) and GhostScript installed. You will also need
the \TeX\ Java Help Library. 

This application uses GhostScript's
\code{/prepress} setting, which is analogous to Acrobat Distiller's
\qt{Prepress Optimized}. This will likely create a larger PDF than
your original.

\begin{warning}
Note that PostScript does not support transparency. If your
PDF file includes transparent elements, the resulting PDF/X file
will end up as a raster image.
\end{warning}

TODO

\chapter{Installation}
\label{sec:install}

If \Jmakepdfx\ is available in your \TeX\ distribution, the best
method of installing it is via your \TeX\ distribution's package
manager. The instructions below are provided in the event that 
\Jmakepdfx\ is not available in your \TeX\ distribution.
To test if \Jmakepdfx\ is correctly installed, run the following in
a command prompt or terminal:
\begin{terminal}
\app{jmakepdfx} \switch{version}
\end{terminal}
This should print the version information.

There are two methods of installation. The first is to install on
the TEXMF tree, where TEXMF denotes the distribution root, for
example \filefmt{/usr/local/texlive/2026/texmf-dist}
or \homefilefmt{texmf} (Unix-like systems) 
or \WindowsOSPath{c:/texlive/2026/texmf-dist} (Windows).

\begin{itemize}
\item TEXMF\filefmt{/scripts/jmakepdfx/jmakepdfx-helpset.tjh}
\item TEXMF\filefmt{/scripts/jmakepdfx/jmakepdfx.jar}
\item TEXMF\filefmt{/scripts/jmakepdfx/jmakepdfx.tlu}
\end{itemize}

The \file{texjavahelplib.jar} library also needs to be installed:
\begin{itemize}
\item TEXMF\filefmt{/scripts/texjavahelp/texjavahelplib.jar}
\end{itemize}
(There will be other files in the \filefmt{texjavahelp}
subdirectory. These are only required if building the
documentation. They are not needed to run \app{jmakepdfx}.)

For Unix-like systems, add a symbolic link to the
\TeX Lua script \file{jmakepdfx.tlu} called
\filefmt{jmakepdfx} somewhere on your system PATH.
This script locates \file{texjavahelplib.jar} and adds it to Java's
class path when running \file{jmakepdfx.jar} (the application jar
file).

On Windows, copy \filefmt{runscript.exe} to \filefmt{jmakepdfx.exe}.
This should find the \file{jmakepdfx.tlu} script and run it.

The second approach is to place \file{texjavahelplib.jar} in the
same directory as \file{jmakepdfx.jar}.
\begin{itemize}
\item \filefmt{jmakepdfx-helpset.tjh}
\item \filefmt{jmakepdfx.jar}
\item \filefmt{texjavahelplib.jar}
\end{itemize}
In this case, the \TeX Lua script is not required and the
\file{jmakepdfx.jar} application can be run as normal for your
system. For example, double-click on the \file{jmakepdfx.jar}
in your filer, if supported, or via the terminal:
\begin{terminal}
java -jar jmakepdfx.jar
\end{terminal}

\chapter{Converting a PDF File}
\label{sec:conversion}

TODO

\chapter{Application Settings}
\label{sec:settings}

TODO

\chapter{Command Line Invocation}
\label{sec:cmdline}

\appdef{jmakepdfx}

\Jmakepdfx\ defaults to \gls{GUI} mode, but it can be run in batch
mode from the command line. The following switches are primarily
intended for batch mode use, but can also be used with the \gls{GUI}
mode, where they will populate or select the corresponding \gls{GUI} fields.

\switchdef{help}
Prints help information to the terminal and exits.

\switchdef{version}
Prints version information to the terminal and exits.
This information includes the version details for
the \TeX\ Java Help Library (\file{texjavahelplib.jar}).

\switchdef{gui}
Switches on the \gls{GUI} mode (default setting).

\switchdef{batch}
Switches on the batch mode setting.

\switchdef{nogui}
A synonym for \switch{batch}.

\switchdef{in}
Specifies the input PDF file. This switch is required for batch mode. With
\gls{GUI} mode, it will set the file in the input file field when the main
\Jmakepdfx\ window is opened.

\switchdef{output}
Specifies the output PDF file. This switch is required for batch mode. With
\gls{GUI} mode, it will set the file in the output file field when the main
\Jmakepdfx\ window is opened.

\switchdef{title}
Sets the PDF title for the output file metadata. If omitted, the title
obtained from the input file will be used, if set.

\switchdef{author}
Sets the PDF author for the output file metadata. If omitted, the author
obtained from the input file will be used, if set.

\switchdef{gray}
Use grayscale profile.

\switchdef{cmyk}
Use CMYK profile.

\switchdef{icc}
Indicates that the ICC file should be used: either the default ICC
file that has previously been saved via the \gls{gui} application
settings, see \sectionref{sec:settings}, or the file specified with
\switch{icc-file} (if set).

\switchdef{noicc}
Indicates that the ICC file should not be used, even if one has been specified.

\switchdef{icc-file}
Specifies the path to the ICC file.

\switchdef{timeout}
Sets the maximum process time (in milliseconds).

\switchdef{rm-tmp}

On exit, removes the temporary PostScript file created by \Jmakepdfx\ that's 
provided for use with the GhostScript process. This setting is the
default.

\switchdef{norm-tmp}

Indicates that the temporary PostScript file created by \Jmakepdfx\
should not be removed on exit. This setting is provided for
debugging if something goes wrong with the GhostScript process.

\switchdef{verbose}

Switches on verbose mode.

\switchdef{noverbose}

Switches off verbose mode.

\switchdef{debug}

Switches on debug mode.

\switchdef{nodebug}

Switches off debug mode.

\printmain

\printindex

\end{document}
